A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-07-23 code/figure2.Rmd

@@

>>>>

###################
## barplot panel ##
###################

load("../data/kelly.colours.rda")
load("../data/moderate_enrich_prob.Rda")

enrich_pathways <- moderate_enrich_prob %>%
  group_by(clust) %>%
  filter(difference > 0.3 & signif <= 2500) %>%
  mutate(pathway = make_clean_names(path)) %>%
  rename(clust_knn = "clust") %>%
  select(clust_knn, pathway) %>%
  mutate(clust_knn = as.numeric(clust_knn)) %>%
  mutate(specific = TRUE)

pathway_counts <- tumor_clusters %>%
  left_join(t(gdc_reactome_path_analysis) %>% 
              as.data.frame() %>% 
              clean_names() %>% 
              rownames_to_column("sample_id")) %>% 
  group_by(clust_knn) %>%
  summarise(total = n(), across(intrinsic_pathway_for_apoptosis:signaling_by_the_b_cell_receptor_bcr, sum)) %>%
  mutate(across(intrinsic_pathway_for_apoptosis:signaling_by_the_b_cell_receptor_bcr, ~ .x / total)) %>%
  select(-total) %>%
  pivot_longer(-clust_knn, names_to = "pathway", values_to = "proportion") %>%
  group_by(clust_knn) %>%
  filter(pathway %in% enrich_pathways$pathway) %>%
  left_join(enrich_pathways %>% select(clust_knn, pathway, specific), by = c("clust_knn", "pathway"))

pathway_counts[is.na(pathway_counts$specific), ]$specific <- FALSE

pathway_mat <- pathway_counts %>%
  select(-specific) %>%
  pivot_wider(names_from = pathway, values_from = proportion) %>%
  ungroup() %>%
  select(-clust_knn) %>%
  as.matrix()

pathway_dist <- dist(t(pathway_mat))
pathway_clust <- as.hclust(rev(as.dendrogram(seriate(pathway_dist, method = "OLO_ward")[[1]])))
pathway_counts$pathway <- factor(pathway_counts$pathway, levels = colnames(pathway_mat)[pathway_clust$order])
bp.cluster.colors <- c(kelly.colours[3:12], "gray15")
names(bp.cluster.colors) <- 1:11

pathway_counts <- pathway_counts %>%
  mutate(color = case_when(specific ~ clust_knn, TRUE ~ 11)) %>%
  mutate(color = factor(color))
save(pathway_counts, bp.cluster.colors, file = "barplot_pathways_fig2b.rda")

@@

load("../barplot_pathways_fig2b.rda")
fig2B <- pathway_counts %>% ggplot(aes(x = pathway, y = proportion, fill = color)) +
  geom_col() +
  facet_wrap(~clust_knn, ncol = 1, strip.position = "right") +
  ylab("Proportion of samples mutated in pathway") +
  xlab("Pathways enriched with mutations within clusters") +
  theme_classic() +
  scale_fill_manual(values = bp.cluster.colors) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.ticks = element_blank(),
    strip.text.y = element_text(size = 12, hjust = .5),
    strip.text.y.right = element_text(angle = 0),
    strip.background = element_blank(),
    legend.position = "none"
  )

fig2B_rotate <- pathway_counts %>% ggplot(aes(y = pathway, x = proportion, fill = color)) +
  geom_col() +
  facet_wrap(~clust_knn, nrow = 1, strip.position = "top") +
  xlab("Proportion of samples mutated in pathway") +
  ylab("Pathways enriched with mutations within clusters") +
  theme_classic() +
  scale_fill_manual(values = bp.cluster.colors) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    axis.ticks = element_blank(),
    strip.text.x = element_text(size = 12, hjust = .5),
    strip.background = element_blank(),
    legend.position = "none"
  )

### 2020-07-23 text/manuscript.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstan)
library(foreach)
library(sqldf)
library(tidyverse)
library(ggthemes)
library(data.table)
library(biomaRt)
library(dplyr)
library(GenomicRanges)
library(SummarizedExperiment)
library(reactome.db)
library(plyr)
library(cluster)
library(pheatmap)
library(clusterProfiler)
library(org.Hs.eg.db)
library(dbscan)
library(class)
library(TCGAbiolinks)
library(patchwork)
library(ggplotify)
library(ComplexHeatmap)
library(knitr)
library(kableExtra)
library(UpSetR)
library(cowplot)
library(doRNG)
library(uwot)
library(janitor)
library(FactoMineR)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstan)
library(foreach)
library(sqldf)
library(tidyverse)
library(ggthemes)
library(data.table)
library(biomaRt)
library(dplyr)
library(GenomicRanges)
library(SummarizedExperiment)
library(reactome.db)
library(plyr)
library(cluster)
library(pheatmap)
library(clusterProfiler)
library(org.Hs.eg.db)
library(dbscan)
library(class)
library(TCGAbiolinks)
library(patchwork)
library(ggplotify)
library(ComplexHeatmap)
library(knitr)
library(kableExtra)
library(UpSetR)
library(cowplot)
library(doRNG)
library(uwot)
library(janitor)
library(FactoMineR)
library(seriation)
```
